%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
% * <hyacinth.ali@mail.mcgill.ca> 2018-05-01T12:22:19.206Z:
%
% ^.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables
\usepackage{subcaption}

% The packages and definition of commands
\usepackage{listings}
\usepackage{color}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{comment}
%\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pifont}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{courier}
\usepackage{booktabs}

\definecolor{almond}{rgb}{0.94, 0.87, 0.8}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
\definecolor{anti-flashwhite}{rgb}{0.95, 0.95, 0.96}
\definecolor{mygreen}{rgb}{0.0, 0.66, 0.35}
\newcommand{\gmReplace}[2]{\textcolor{red}{GM replaced: }\textcolor{blue}{#1}{\textcolor{red}{\ with }\textcolor{mygreen}{#2}}}
\newcommand{\haReplace}[2]{\textcolor{green}{HA replaced: }\textcolor{red}{#1}{\textcolor{blue}{\ with }\textcolor{mygreen}{#2}}}
\newcommand{\haAction}[1]{\textcolor{blue}{#1}}
\newcommand{\haActionInProgress}[1]{\textcolor{asparagus}{#1}}
\newcommand{\haDeleted}[1]{\textcolor{green}{HA deleted} \textcolor{red}{#1}}
\newcommand\tab[1][1cm]{\hspace*{#1}}


%\renewcommand \gmReplace[2]{}
%\renewcommand \haReplace[2]{}



% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[MODELS 2018]{ACM/IEEE 21st International Conference on Model Driven Engineering Languages and Systems}{October 2018}{Copenhagen, Denmark}
\acmYear{2018}
\copyrightyear{2018}


\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%.....................................................%
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}


\begin{document}
\title{Layout Merging with Relative Positioning \\ Case Study : Concern Oriented Layout}

\author{Hyacinth Ali}
\affiliation{%
  \institution{McGill University}
  \streetaddress{845 Sherbrooke St.}
  \city{Montreal}
  \state{Quebec}
  \postcode{H3A 0G4}
}
\email{hyacinth.ali@mail.mcgill.ca}

\author{Gunter Mussbacher}
\affiliation{%
  \institution{McGill University}
  \streetaddress{845 Sherbrooke St.}
  \city{Montreal}
  \state{Quebec}
  \postcode{H3A 0G4}
}
\email{gunter.mussbacher@mcgill.ca}


% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{H. Ali, G. Mussbacher}


\begin{abstract}
The advent of modeling in software engineering, like other engineering fields, has revolutionized the formalism and pace of software development. However, software applications are not built from scratch, instead, other existing software artifacts are reused and combined with new artifacts. This notion of software reuse has been in existence for decades. When structural models such as class diagrams are reused, the reusing and reused models often need to be merged and the result visualized to the modeler. However, state-of-the-art layout mechanisms such as GraphViz, \haAction{and other related layout tools,} do not retain the original layout and rather arbitrarily layout the merged models. Therefore, important information conveyed by the specific layout is currently lost. This paper aims to establish a robust layout algorithm called rpGraph that retains the general layout of the reusing and reused models after merging. rpGraph uses the relative positioning of model elements to inform the positioning of merged model elements. Our findings are evaluated with 20 example model reuses from a library of reusable software model artifacts. \haAction{A case study is also carried out in Concern Oriented Reuse (CORE), where rpGraph is applied to layout different configuration of concern feature selection. In each case,} a comparison of the merged layouts of rpGraph, GraphViz, and JGraphX shows that rpGraph performs better in terms of retaining the original layouts and \haAction{mental map of the modeler.} 
\end{abstract}
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011060.10011063</concept_id>
<concept_desc>Software and its engineering~System modeling languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011074.10011092.10011096</concept_id>
<concept_desc>Software and its engineering~Reusability</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~System modeling languages}
\ccsdesc[500]{Software and its engineering~Reusability}

\keywords{Relative Positioning, Automatic Layout, Software Reuse, Model Composition, Class Diagram}

\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
